$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-05-11 paper/e6ssm-tuning-paper.tex
Added missing math delimiters around SU(5), and changed line lengths
to comply with APS guidelines for submissions

In general though it is possible for gauge kinetic mixing to be much larger as can be the case if one considers an additional $5 + \overline{5}$ pair of SU(5) multiplets \cite{Rizzo:1998ut} or as has been looked in the $U(1)_{B-L}$ \cite{Salvioni:2009mt,Krauss:2012ku}.  In such a case this will  impact the results in two ways, firstly by altering the $Z^\prime$ limit from experiment and secondly by altering the charges which appear in the EWSB condition, which can be seen from examining Eqs.~(\ref{eq:originalE6MZequation})-(\ref{eq:ddefn}).

>>>>

In general though it is possible for gauge kinetic mixing to be much larger
as can be the case if one considers an additional $5 + \overline{5}$ pair of
$SU(5)$ multiplets \cite{Rizzo:1998ut} or as has been looked in the $U(1)_{B-L}$
\cite{Salvioni:2009mt,Krauss:2012ku}.  In such a case this will impact the
results in two ways, firstly by altering the $Z^\prime$ limit from experiment
and secondly by altering the charges which appear in the EWSB condition,
which can be seen from examining
Eqs.~(\ref{eq:originalE6MZequation})-(\ref{eq:ddefn}).
